---
title: "R Data Types"
Date  :
---

1. Vector

```{r}
x <- c(1,2,3,4,5,6,7,8,9,10,11,12,34,56,75,32,67,77)
print(x)
```
```{r}
y <- c("one","Two","Three","Four","Five","Six")
print(y)
print(class(y)) # High level
print(typeof(y)) # Low Level

```
Indexing (I R index starts from 1 while most other languages starts from 0)
```{r}
print(y[2])  #print element at index no 2

```
In R, negative indexing is used to exclude specific elements from a vector. By specifying negative indices, you tell R to return all elements except those at the specified positions.
```{r}
print(y[-2]) # Remove element at index 2
print(y[c(-3,-4)]) # Remove elemens at index 3 and 4
```
Mixed types in a vector
```{r}
s <- c('apple','red',5,TRUE)
typeof(s)
print(s)
```
Creating Vector using sequence seq()


```{r}
seq_var <- seq(5,9, by=1)
print(seq_var)

yyy <- seq(5,9, by=0.6)
print(yyy)

```
Creating a Vector using range

```{r}
v <- 5:13
print(v)
```
Creating a sequence from 5.6 to 12.6
```{r}
rv <- 5.6 : 12.6
print(rv)

rsv <- seq(5.6,12.6, by=1)
print(rsv)

```
```{r}

```
```{r}
weekdays <- c("Sun","Mon","Tue","Wed","Thu","Fri","Sat")
print(weekdays)
weekdays

#Using Logical indexing to access vector elements

```
```{r}
#install.packages("pryr")
library(pryr)
x <- 42
address(x)
```
Vector Operatios
```{r}
vec1 <- c(4,5,6,7,8)
vec2 <- c(2,3,4,5,6)

addRes <- vec1 + vec2
subRes <- vec1 - vec2
mulRes <- vec1 * vec2
divRes <- vec1 / vec2
print(addRes)
print(subRes)
print(mulRes)
print(divRes)

```
Vector Element Recycling
```{r}
v1 <- c(5,1,4,8)
v2 <- c(3,2)
add.result <- v1+v2

v11 <- c(2,2,2)
v22 <- c(1,2,3,4,5,6)
add.result1 <- v11 - v22
print(add.result1)
help(readline())
```
Read Element from the keyboard
```{r}
name <- readline(prompt = "Enter your name: ")
cat("Hello,", name, "!\n")
```
